\documentclass[9pt]{article}
\usepackage{outline}
\usepackage[footskip=0.05in]{geometry}
\title {Towards Fog-aware Kubernetes}
\date{}
\pagestyle{empty}

\begin{document}
\maketitle

	\begin{outline}
		\item {\bf Abstract {\em (to be determined later)}}
		\item {\bf Introduction }
  		\begin{outline}
			\item {\bf Fog Computing Concept.} 
    		\begin{outline}
    			\item The introduction of Fog computing.
    			\item The resource Fog provide.
    			\item Fog targeted application and user proximity. 
    			\item Platforms for fog. 
    		\end{outline}
    		\item {\bf Kubernetes}
    		\begin{outline}
				\item Kubernetes and Clouds.
				\item Why Kubernetes is not compatible with Fog computing (briefly).      	
    	
    		\end{outline}
    	\item {\bf Organization } \\
      		Explain organization of the report, what is included, and what is not.
     \end{outline}
    		
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END OF INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    		

	\item {\bf Kubernetes and Fog computing. }
	\begin{outline}
	\small (Divided into sections that will be treated separately)
		\item Kubernetes backbone components:
			\begin{itemize}
				\item pods.
				\item deployment controllers. 
				\item services.
				\item Load-balancers, scheduling, ... 
			\end{itemize}
		\item Advantages:
		\begin{itemize}
			\item Community.
			\item Scalability.
			\item Containerized.
			\item Clean separation between the app and the system.
			\item Distribution  
		\end{itemize}
		
		\item Disadvantages: 
		\begin{itemize}
			\item Centralization.
			\item Location awareness.
			\item Bad load balancing allocations doesn't consider the latency.
			\item Scheduling regardless the location.
		\end{itemize}
	\end{outline}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END OF PROBLEM DECLARATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item {\bf  A Road map towards a Fog aware Kubernetes}
	\begin{outline}
		\item The decentralization.
		\item Location awareness. 
		\item Scheduling schemes.
				
	\end{outline}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END OF PROPOSED MECHANISM AND RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%
	\item {\bf Conclusion. {\em (to be determined later)}}
	\item {\bf Acknowledgement.}



	

\end{outline}

\end{document}